---
title: "TidyTemplate"
date: 2022-06-14
output: html_document
---

# TidyTuesday

Join the R4DS Online Learning Community in the weekly #TidyTuesday event!
Every week we post a raw dataset, a chart or article related to that dataset, and ask you to explore the data.
While the dataset will be “tamed”, it will not always be tidy! As such you might need to apply various R for Data Science techniques to wrangle the data into a true tidy format.
The goal of TidyTuesday is to apply your R skills, get feedback, explore other’s work, and connect with the greater #RStats community!
As such we encourage everyone of all skills to participate!

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

library(tidytuesdayR)
library(tidyverse)
library(lubridate)
library(usefunc)
library(geofacet)
library(ggstream)
library(forcats)
library(showtext)

# load fonts
font_add_google(name = "Bowlby One SC", family = "bowlby")
font_add_google(name = "Ubuntu", family = "ubuntu")
showtext_auto()
```

# Load the weekly Data

Download the weekly data and make available in the `tt` object.

```{r Load}
# load data
drought <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2022/2022-06-14/drought.csv')


drought
```


# Wrangle

Explore the data and process it into a nice format for plotting! Access each dataset by name by using a dollarsign after the `tt` object and then the name of the data set.

```{r Wrangle}
# prep data
plot_data <- drought %>% 
  select(DATE, state, D0, D1, D2, D3, D4) %>% 
  # fix date
  mutate(date = parse_number(DATE), 
         date = ymd(date)) %>% 
  mutate(year = year(date)) %>% 
  select(-c(DATE, date)) %>% 
  # fix state names
  mutate(state = str_replace(state, pattern = "-", replacement = " "), 
         state = str_to_title(state)) %>% 
  mutate(state_abb = US_name_to_abb(state)) %>% 
  select(-state) %>% 
  pivot_longer(D0:D4, values_to = "perc", names_to = "level") %>% 
  # average per year
  mutate(decade = floor(year/10)*10) %>% 
  group_by(decade, state_abb, level) %>% 
  mutate(mean_perc = mean(perc)) %>% 
  select(-c(year, perc)) %>% 
  # levels as factor
  mutate(level = factor(level), 
         level = fct_rev(level)) %>% 
  ungroup() %>% 
  complete(level, decade, state_abb) %>% 
  distinct()

# plot viewer
dev.new(width=12,height=8,unit="in", noRStudioGD = TRUE)
```


# Visualize

Using your processed dataset, create your unique visualization.

```{r Visualize}
# plot
ggplot(data = plot_data, 
       mapping = aes(x = decade, y = mean_perc, fill = level)) +
  geom_stream(type = "ridge", extra_span = .1) + 
  geom_text(data = filter(plot_data, decade == 1960, level == "D0"), 
            aes(x = 1960, y = 35, label = state_abb), 
            family = "bowlby", size = 5, hjust = 0.5, 
            colour = alpha("#808080", 0.5)) +
  facet_geo(~state_abb, grid = "us_state_contiguous_grid1") +
  scale_fill_brewer(palette = "YlOrRd", direction = -1, 
                    breaks = c("D0", "D1", "D2", "D3", "D4"), 
                    labels = str_wrap(c("Abnormally dry", 
                               "Moderate drought", 
                               "Severe drought", 
                               "Extreme drought", 
                               "Exceptional drought"), 10)) +
  scale_x_continuous(breaks = c(1920, 1980)) +
  labs(x = "", 
       y = "", 
       title = "US Droughts", 
       caption = "Oluwafemi Oyedele | Data: National Integrated Drought Information System") +
  coord_cartesian(expand = FALSE) +
  theme(plot.background = element_rect(fill = "#fafafa", colour = "#fafafa"), 
        panel.background = element_rect(fill = "#fafafa", colour = "#fafafa"), 
        legend.background = element_rect(fill = "#fafafa", colour = "#fafafa"), 
        legend.position = "right",
        legend.title = element_blank(), 
        panel.grid = element_blank(), 
        axis.text.y = element_blank(), 
        axis.ticks = element_blank(), 
        strip.background = element_blank(), 
        strip.text = element_blank(),
        plot.title = element_text(family = "serif", size = 30, hjust = 0.5, 
                                  colour = "gray", margin = margin(t = 10, b = 10)), 
        legend.text = element_text(family = "ubuntu", size = 10, hjust = 0.5, 
                                  colour = "#808080"), 
        plot.caption = element_text(family = "ubuntu", size = 10, hjust = 0.5, 
                                   colour = "#808080", margin = margin(t = 10, b = 10)), 
        axis.text.x = element_text(family = "ubuntu", size = 10, hjust = 0.5, 
                                               colour = "#808080")
        )


  
```

# Save Image

Save your image for sharing. Be sure to use the `#TidyTuesday` hashtag in your post on twitter! 

```{r}

# This will save your most recent plot
ggsave(
  "Week_24.png",
  path = here::here('2022/2022-06-14-Week-24'))

```
