---
title: "TidyTemplate"
date: 2022-06-21
output: html_document
---

# TidyTuesday

Join the R4DS Online Learning Community in the weekly #TidyTuesday event!
Every week we post a raw dataset, a chart or article related to that dataset, and ask you to explore the data.
While the dataset will be “tamed”, it will not always be tidy! As such you might need to apply various R for Data Science techniques to wrangle the data into a true tidy format.
The goal of TidyTuesday is to apply your R skills, get feedback, explore other’s work, and connect with the greater #RStats community!
As such we encourage everyone of all skills to participate!


```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(geomtextpath)
library(ggforce)
library(tidytuesdayR)


#gg_record(dir = "2022/2022-06-14-Week-24", device = "png", width = 10, height = 8, units = "in", dpi = 320)
```

# Load the weekly Data

Download the weekly data and make available in the `tt` object.

```{r Load}

slave_routes <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-06-16/slave_routes.csv')

```


# Readme

Take a look at the readme for the weekly data to get insight on the dataset.
This includes a data dictionary, source, and a link to an article on the data.

```{r Readme, eval = interactive()}

tt

```


# Glimpse Data

Take an initial look at the format of the data available.

```{r Glimpse}

slave_routes %>% 
  map(glimpse)

```

# Wrangle

Explore the data and process it into a nice format for plotting! Access each dataset by name by using a dollarsign after the `tt` object and then the name of the data set.

```{r Wrangle}
decade_routes <- slave_routes %>% 
  mutate(
    decade = year_arrival - year_arrival %% 10
  ) %>% 
  group_by(decade) %>% 
  summarise(
    total = sum(n_slaves_arrived, na.rm = TRUE),
    routes = n()
    ) %>% 
  ungroup() 

peak <- decade_routes %>% 
  filter(between(decade, 1750, 1820)) %>% 
  summarise(total = sum(total))

f1 <- "Quotes Caps"
f2 <- "Sora"

# String for chain
chain = paste(rep("o-", 315), collapse = "")

```


# Visualize

Using your processed dataset, create your unique visualization.

```{r Visualize}
ggplot(decade_routes, aes(routes, total)) +
  # Annotation for 1750-1820
  geom_mark_circle(aes(filter = between(decade, 1750, 1820), description = str_wrap(paste(round(peak$total/1e6, 1), "million people were transferred between 1750 and 1820"), 22)), color = "salmon3", label.colour = "white", con.colour = "salmon3", label.fill = NA, size = 0.4, con.size = 0.2, label.fontsize = 9, label.family = f2, label.hjust = 1, con.type = "none", linetype = "dotted") +
  # Decade markers
  geom_point(aes(size = if_else(decade %% 100 == 0, 5, 2.5)), color = "salmon1") +
  # Chain
  geom_textpath(label = chain, size = 2.5, fontface = "bold", color = "grey85") +
  # Decade labels
  ggrepel::geom_text_repel(data = subset(decade_routes, decade %% 50 == 0), aes(label = decade), nudge_x = 100, nudge_y = -10000, hjust = 0, size = 8, family = f1, point.padding = 0.75, segment.size = 0.2, color = "white") +
  # Subtitle
  annotate("text", 50, 475000,
    label = str_wrap(
      "More than 12 million enslaved Africans were forcibly transferred across the Atlantic by European colonizers over a span of 400 years. Approximately 1.2–2.4 million died during the voyage. The graphic shows the number of slaves transported by decade (of a total of about 5 million people), as documented in the records of more than 36 000 voyages between 1514 and 1866.", 55), hjust = 0, vjust = 1, size = 4, colour = "white", family = f2) +
  # Title
  annotate("text", 50, 5.12e5, label = "TRANS-ATLANTIC SLAVE TRADE", hjust = 0, vjust = 1, size = 10, colour = "coral1", family = f1) +
  # Caption
  annotate("text", 1550, 1e4,
    label = "SOURCE: SLAVE VOYAGES & WIKIPEDIA · GRAPHIC: OLUWAFEMI OYEDELE", hjust = 0, vjust = 1, size = 2.5, colour = "grey50", family = f2) +
  scale_size_identity() +
  scale_x_continuous(labels = scales::label_number_auto(), breaks = c(1e3, 2e3, 3e3)) +
  scale_y_continuous(labels = scales::label_number_auto(), breaks = seq(1e5, 5e5, 1e5)) +
  coord_cartesian(clip = "off") +
  labs(
    x = "Voyages per decade",
    y = "Slaves transferred per decade"
  ) +
  theme_minimal(base_family = f2) +
  theme(
    plot.background = element_rect(fill = "grey10", color = NA),
    plot.margin = margin(20, 20, 20, 20),
    panel.grid = element_line(color = "grey25"),
    panel.grid.major = element_line(size = 0.3),
    panel.grid.minor = element_line(size = 0.15),
    axis.text = element_text(color = "grey60"),
    axis.title = element_text(color = "grey90"),
    axis.title.x = element_text(margin = margin(10, 0, 0, 0)),
    axis.title.y = element_text(margin = margin(0, 10, 0, 0))
  )
```

# Save Image

Save your image for sharing. Be sure to use the `#TidyTuesday` hashtag in your post on twitter! 

```{r}

# This will save your most recent plot
ggsave('Slave_Route.png',width = 11,height = 9,dpi = 450,path = 2022-06-21-Week-25')
```
